---
title: "Preliminary results of the impact evaluation paper"
author: "Mani Rouhi Rad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
#output: pdf_document
#output: md_document
output: 
  html_document:
    css: custom.css
#    keep_md: true
#fontsize: 12pt
---


```{r, include=FALSE, warning=FALSE}
library(rgeos)
library(rgdal)
library(plyr)
library(reshape2)
library(dplyr)
library(data.table)
library(ggplot2)
library(scales)
library(R.matlab)
library(sp)
library(sf)
library(maptools)
library(broom)
library(quantreg)
library(foreign)
library(raster)
library(lmtest)
library(RColorBrewer)
library(readstata13)
library(parallel)
require(stargazer)
library(AER)
library(texreg)
library(gridExtra)
library(grid)

```


```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = 'C:/Users/mr2284/Dropbox/Panama S2/Impact Evaluation')
knitr::opts_knit$set(root.dir = 'C:/Users/mr2284/Dropbox/Research/Panama Canal-My material/Codes/IE/IE_PCW')
# knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='./Figures and Tables', echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```


```{r, include=FALSE, warning=FALSE}
simpleCap <- function(x) {                                          # 1) Function defined to make all caps to propper
  paste(substring(x, 1,1), tolower(substring(x, 2)),                # 2)
        sep="")                       }                             # 3)

FN_area_sp = function(input_sp, scenario){                          # 1) function defined to find the area
  foo = st_as_sf(input_sp)
  a = as.data.table(input_sp@data)
  b = as.data.table(st_area(foo))
  b[, paste(scenario, "ha", sep="_"):=as.numeric(x*0.0001)]
  b=b[, 2]
  output_data=data.table(a, b)
  return(output_data)
}

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

grid_arrange_shared_legend <- function(...) {
  plots <- list(...)
  g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  grid.arrange(
    do.call(arrangeGrob, lapply(plots, function(x)
      x + theme(legend.position="none"))),
    legend,
    ncol = 1,
    heights = unit.c(unit(1, "npc") - lheight, lheight))
    # heights=unit(c(2, 2, 2), c("in", "in", "in")))

}

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
########                                  Input data    ######
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#                   I. River discharge
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# river_discharge=data.table(read.csv("./Data/Map Area_update.csv"))
river_discharge=data.table(read.csv("./Data/Map Area2.csv"))
river_discharge=melt(river_discharge, id=c("River", "Year", "Day"), variable.name = "month", value.name = "discharge_m3_s")
river_discharge=river_discharge[complete.cases(Day)]
river_discharge[ , month:=as.character(month)]
river_discharge[ , month:=match(month,month.abb)]

# river_discharge[, foo_date:=as.character(paste(Year, month, Day, sep = "/"))]
# river_discharge[, date_read := as.Date(foo_date, "%Y/%b/%d")]
river_discharge=river_discharge[,.(River, year=Year, month, day=Day, discharge_m3_s)]
river_discharge[, discharge_m3_s:=as.numeric(discharge_m3_s)]

river_discharge[, River:=gsub("Cano", "Cano Quebrado", River)]
river_discharge[, River:=gsub("Ciri", "Ciri grande", River)]
river_discharge[, unique(River)]


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#                   II. River - watershed connection
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
river_names              = readOGR(dsn="./Data/Rivers",layer="Rivers_PCWCopy")
river_names=data.table(river_names@data)
river_names=river_names[,.(NOMBRE, SUBCUENC_2)]

river_names[, River:=simpleCap(NOMBRE)]
spanish_cano=river_names[, unique(River)][3]
river_names[, River:=gsub(spanish_cano, "Cano Quebrado", River)]
river_names[, unique(River)]

setkey(river_names,     River)
setkey(river_discharge, River)

river_discharge=river_names[river_discharge]
river_discharge=river_discharge[complete.cases(NOMBRE)]
river_discharge=river_discharge[,.(River, SUBCUENC_2, year, month, day, discharge_m3_s)]

weird_char = unique(river_discharge$SUBCUENC_2)[1]
weird_char = substr(weird_char, 1, 4) # win
# weird_char = substr(weird_char, 1, 3) # mac

river_discharge[, SUBCUENC_2 := gsub(weird_char, "Rio", SUBCUENC_2)]
river_discharge[, SUBCUENC_2 := gsub("Boquerón", "Boqueron", SUBCUENC_2)]
river_discharge[, SUBCUENC_2 := gsub("Caño", "Cano", SUBCUENC_2)]

weird_char_ciri=unique(river_discharge$SUBCUENC_2)[4]
weird_char_ciri=substr(weird_char_ciri, 5, 8)
weird_char_pequeni=unique(river_discharge$SUBCUENC_2)[6]
weird_char_pequeni=substr(weird_char_pequeni, 5, 13)
river_discharge[, SUBCUENC_2 := gsub(weird_char_ciri,    "Ciri",    SUBCUENC_2)] # win
river_discharge[, SUBCUENC_2 := gsub(weird_char_pequeni, "Pequeni", SUBCUENC_2)] # win
river_discharge[, SUBCUENC_2 := gsub("Gatún", "Gatun", SUBCUENC_2)]
river_discharge[, unique(SUBCUENC_2)]

river_discharge[year==2016 & River=="Gatun",.N, by="month"]
river_discharge[year==2016 & River=="Chagres",.N, by="month"]
river_discharge[,.N, by=River]

# Except Indio, which will be thrown out, the panel is almost balanced. Only Chagres has more data which may mean there is "extra" data
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#                   II. Hectares in each region-year
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
PIEA                 = readOGR(dsn="./Data/PIEA",       layer="PIEA_polygons")
watershed_original   = readOGR(dsn="./Data/Watersheds", layer="Watersheds_PCW")
watershed_original   = gBuffer(watershed_original,    byid = TRUE, width = 0)
watershed_PIEA_final = raster::intersect(PIEA, watershed_original)
# writeOGR(watershed_PIEA_final, 
#          dsn="./Data/PIEA", layer="PIEA_by_watershed", driver="ESRI Shapefile")


watershed_PIEA_final=FN_area_sp(watershed_PIEA_final, "area_PIEA_watershed")
watershed_PIEA_final=watershed_PIEA_final[,.(Uso, SUBCUENC_2, area_PIEA_watershed_ha, area_watershed_ha=area_Water)]
watershed_PIEA_final[, Uso:=gsub(": Programa PIEA", "", Uso)]
watershed_PIEA_final_by_land_use = watershed_PIEA_final[,   sum(area_PIEA_watershed_ha),                          by="Uso"]
watershed_PIEA_final_by_watershed= watershed_PIEA_final[, .(sum(area_PIEA_watershed_ha), sum(area_watershed_ha)), by="SUBCUENC_2"]
watershed_PIEA_final_by_watershed[, percent_area:=V1/V2*100]
setkey(watershed_PIEA_final_by_watershed, percent_area)

watershed_PIEA_final[, SUBCUENC_2 := gsub(weird_char, "Rio", SUBCUENC_2)]
watershed_PIEA_final[, SUBCUENC_2 := gsub("Boquerón", "Boqueron", SUBCUENC_2)]
watershed_PIEA_final[, SUBCUENC_2 := gsub("Caño", "Cano", SUBCUENC_2)]
watershed_PIEA_final[, SUBCUENC_2 := gsub(weird_char_ciri, "Ciri", SUBCUENC_2)]
watershed_PIEA_final[, SUBCUENC_2 := gsub(weird_char_pequeni, "Pequeni", SUBCUENC_2)] # mac
watershed_PIEA_final[, SUBCUENC_2 := gsub("Gatún", "Gatun", SUBCUENC_2)]
watershed_PIEA_final[, unique(SUBCUENC_2)]


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#                   III. Rainfall (Other climatic variables?)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

################
# rainfall_PIEA=read.dta13("./Data/Rainfall/acp_15Minstorms_Steve_v18112016.dta")
# rainfall_PIEA=data.table(rainfall_PIEA)
# rainfall_PIEA[,month:=substr(date, 4, 5)]
# rainfall_PIEA[,day  :=substr(date, 1, 2)]
# rainfall_PIEA[,total_rain_day:=sum(Totalrain), by=c("site", "Year", "month", "day")]
# rainfall_PIEA=unique(rainfall_PIEA, by=c("site", "Year", "month", "day"))
# rainfall_PIEA[,month:=as.numeric(month)]
# rainfall_PIEA[,Year :=as.numeric(Year)]
# rainfall_PIEA[,day  :=as.numeric(day)]

################
rainfall_PIEA2=read.csv("./Data/Rainfall/ACP_Rainfall_hourly.csv")
rainfall_PIEA2=data.table(rainfall_PIEA2)
rainfall_PIEA2[,DATETIME.dd.mm.yyyy.hh.mm.:=as.character(DATETIME.dd.mm.yyyy.hh.mm.)]
rainfall_PIEA2[, day:=substr(DATETIME.dd.mm.yyyy.hh.mm., 1, regexpr('/', DATETIME.dd.mm.yyyy.hh.mm.)-1)]
rainfall_PIEA2[,first_foo:=substr(DATETIME.dd.mm.yyyy.hh.mm., regexpr('/', DATETIME.dd.mm.yyyy.hh.mm.)+1, 20)]
rainfall_PIEA2[, month:=substr(first_foo, 1, regexpr('/', first_foo)-1)]
rainfall_PIEA2[,first_foo:=substr(first_foo, regexpr('/', first_foo)+1, 20)]
rainfall_PIEA2[, year:=substr(first_foo, 1, regexpr(' ', first_foo)-1)]

rainfall_PIEA2[, day:=  as.numeric(as.character(day))]
rainfall_PIEA2[, month:=as.numeric(as.character(month))]
rainfall_PIEA2[, year:= as.numeric(as.character(year))]
rainfall_PIEA2=rainfall_PIEA2[, .(Station, year, month, day, total_rain_day=Rain..mm.)]
rainfall_PIEA2[, total_rain_day:=sum(total_rain_day), by=c("Station", "year", "month", "day")]
rainfall_PIEA2=unique(rainfall_PIEA2, by=c("Station", "year", "month", "day"))

####### check these two for rainfall before 2004
rainfall_PIEA2[,unique(Station)]

rainfall_PIEA2[Station== "CHORRO", .N, by="year"]


# for (i in 1:nrow(rivers_used)) {
#   temp=rainfall_PIEA2[Station== rivers_used[i], .N, by="year"]
#   print(rivers_used[i])
#   print(temp)
#   readline(prompt="Press [enter] to continue")
# }
######## only SANMIGUEL and CHAGRECITO don't have enough data. Unfortunately, ZANGUENA only has data starting 2004. This is in Cano Quebrado catchment so would have been helpful.
setnames(rainfall_PIEA2, "Station", "site")
###############


rainfall_stations = readOGR(dsn="./Data/Rainfall/stations", layer="stations")
# foo1 = watershed_original[!is.na(over(rainfall_stations, as(watershed_original,"SpatialPolygons"))),]

bar_1=over(rainfall_stations, as(watershed_original,"SpatialPolygons"))
bar_1=data.table(bar_1)
setnames(bar_1, "bar_1", "over_id")
bar_2=data.table(bar_1, rainfall_stations@data)
bar_2=bar_2[complete.cases(over_id)]
bar_3=data.table(watershed_original@data)

setkey(bar_2, over_id)
setkey(bar_3, OBJECTID_1)
bar= bar_2[bar_3]
bar=bar[complete.cases(CODENAME)]
setkey(bar, CODENAME)
rainfall_stations=bar[,.(OBJECTID, over_id, CODENAME, SUBCUENC_2)]
rainfall_stations[, CODENAME:=gsub(" ", "", CODENAME, fixed = TRUE)]
setkey(rainfall_stations, CODENAME)
setkey(rainfall_PIEA2, site)
rainfall_PIEA2=rainfall_stations[rainfall_PIEA2]
rainfall_PIEA2=rainfall_PIEA2[complete.cases(CODENAME) & complete.cases(SUBCUENC_2)]
rainfall_PIEA2=rainfall_PIEA2[,.(Station= CODENAME, SUBCUENC_2, date=as.Date(paste(year, month, day, sep = "-")), year, month, day, total_rain_day)]
# rainfall_PIEA2[, date_read:=as.Date(date, "dd/mm/yyyy")]
# rainfall_PIEA2[, date_read:=as.Date(date, "%d/%m/%Y")]

# 
# ggplot(data = rainfall_PIEA2[Station=="CANONES"], aes(x=date_read, y=total_rain_day))+
#   geom_line(size=1.1)+
#   # coord_cartesian(ylim=c(0, 400)) +
#   scale_x_date(labels = date_format("%m-%Y")) #+ 
# # scale_y_discrete(breaks=seq(0, 400, 100))  # Ticks from 0-10, every .25
# rainfall_PIEA2[, unique(Station)]

rainfall_PIEA2[,        unique(SUBCUENC_2)]
# watershed_PIEA_final[, unique(SUBCUENC_2)]
# river_discharge[, unique(SUBCUENC_2)]
# str(river_discharge)
# str(rainfall_PIEA2)

rainfall_PIEA2[SUBCUENC_2== rainfall_PIEA2[,        unique(SUBCUENC_2)][6], unique(Station)]
rainfall_PIEA2[Station   == rainfall_PIEA2[SUBCUENC_2==rainfall_PIEA2[,        unique(SUBCUENC_2)][6], unique(Station)]]
# rainfall_PIEA[Station  == rainfall_PIEA2[SUBCUENC_2==rainfall_PIEA2[,        unique(SUBCUENC_2)][6], unique(Station)]]
### looks good \/

rainfall_PIEA2[, SUBCUENC_2 := gsub(weird_char, "Rio", SUBCUENC_2)]
rainfall_PIEA2[, SUBCUENC_2 := gsub("Boquerón", "Boqueron", SUBCUENC_2)]
rainfall_PIEA2[, SUBCUENC_2 := gsub("Caño", "Cano", SUBCUENC_2)]
rainfall_PIEA2[, SUBCUENC_2 := gsub(weird_char_ciri, "Ciri", SUBCUENC_2)] # win
rainfall_PIEA2[, SUBCUENC_2 := gsub(weird_char_pequeni, "Pequeni", SUBCUENC_2)] # win
rainfall_PIEA2[, SUBCUENC_2 := gsub("Gatún", "Gatun", SUBCUENC_2)]
rainfall_PIEA2[, unique(SUBCUENC_2)]

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#                   IV. Seasons
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
seasons=read.csv("./Data/seasons.csv")
seasons=data.table(seasons)
seasons[, Dry_season_start_date := as.Date(Dry_season_start, "%d-%b-%y")]
seasons[, Dry_season_end_date   := as.Date(Dry_season_end,   "%d-%b-%y")]
seasons=seasons[,.(YEAR, Dry_season_start_date, Dry_season_end_date)]
seasons[, Dry_season_length := Dry_season_end_date - Dry_season_start_date]

setkey(seasons, YEAR)
setkey(river_discharge, year)


river_discharge=river_discharge[seasons]
river_discharge=river_discharge[complete.cases(River)]
river_discharge[, date_disch:=as.Date(paste(year, month, day, sep = "/"))]
river_discharge=river_discharge[complete.cases(date_disch)]
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#                   V. Merge
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
setkey(rainfall_PIEA2,  SUBCUENC_2, year, month, day)
setkey(river_discharge, SUBCUENC_2, year, month, day)

unique(rainfall_PIEA2,  by="SUBCUENC_2")
unique(river_discharge, by="SUBCUENC_2")

# setkey(watershed_PIEA_final, SUBCUENC_2, year, month, day)
# setkey(watershed_PIEA_final, SUBCUENC_2, Uso)

# data_reg = river_discharge[rainfall_PIEA2, allow.cartesian=T, all.x=T]
# data_reg = rainfall_PIEA2[river_discharge, allow.cartesian=T]
# data_reg = data_reg[complete.cases(date_read)]
# data_reg = data_reg[complete.cases(total_rain_day) & complete.cases(discharge_m3_s)]

data_reg = merge(river_discharge, rainfall_PIEA2, by.x=c("SUBCUENC_2", "year", "month", "day"), by.y=c("SUBCUENC_2", "year", "month", "day") , all.x=T)
# data_reg = data_reg[year > 2004]
data_reg = data_reg[year > 2003]
data_reg = data_reg[,.(SUBCUENC_2, River, year, month, day, Dry_season_start_date, Dry_season_end_date, discharge_m3_s, Station, total_rain_day)]
data_reg[, date_read := as.Date(paste(year, month, day, sep = "-"))]
data_reg=data_reg[complete.cases(date_read)]
data_reg[is.na(total_rain_day), total_rain_day:=0]

# rivers_used=data_reg[, unique(Station), by="SUBCUENC_2"]
# rivers_used=rivers_used[,2]
data_reg[, day_of_dry_season := date_read - Dry_season_start_date]
data_reg[, day_of_wet_season := date_read - (Dry_season_end_date+1)]
data_reg[, day_of_season     := ifelse(date_read < Dry_season_end_date+1, day_of_dry_season, day_of_wet_season)]
data_reg[, dry_dummy         := ifelse(date_read < Dry_season_end_date+1, 1, 0)]
data_reg=data_reg[year<2016]

######## I think merging discharge and rainfall should be done more carefully



#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#                   VI. land use data
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# These are the areas that Blair estimated. I double chekced Trinidad for 2012 and the estimates look good. So I am using the estimates.
# 
land_use=read.csv("./Data/Land Covers/land_use_over_time_R_input.csv")
land_use=data.table(land_use)
land_use[, unique(River)]
land_use=land_use[River!="Las Cascadas"]

land_use=land_use[,foo:=ifelse(X2003==0 & X2008==0 & X2012==0, 1, 0)]
land_use=land_use[foo==0]
land_use=land_use[Land.use!="Water"]



forest=land_use[Land.use=="Mature Forests" | Land.use=="Secondary Forests" | Land.use=="Forest Plantations"]
cols=colnames(forest)[3:5]
forest[, (cols):=lapply(.SD, sum), by="River", .SDcols=cols] 
forest=unique(forest, by="River")
forest=forest[,.(River, f_2003=X2003, f_2008=X2008, f_2012=X2012)]


non_forest=land_use[Land.use=="Pastures" | Land.use=="Crops" | Land.use=="Scrub" | Land.use=="Kans Grass" | Land.use=="Towns" | Land.use=="Barren Soil"]
cols=colnames(non_forest)[3:5]
non_forest[, (cols):=lapply(.SD, sum), by="River", .SDcols=cols] 
non_forest=unique(non_forest, by="River")
non_forest=non_forest[,.(River, n_2003=X2003, n_2008=X2008, n_2012=X2012)]

setkey(forest, River)
setkey(non_forest, River)
net=forest[non_forest]
net[, X2003:=f_2003 - n_2003]
net[, X2008:=f_2008 - n_2008]
net[, X2012:=f_2012 - n_2012]
net=net[,.(River, type="net", X2003, X2008, X2012)]

land_use_fig = copy(land_use)
land_use_fig[, type:=ifelse(Land.use=="Mature Forests" | Land.use=="Secondary Forests" | Land.use=="Forest Plantations", "forest", 
                            ifelse(Land.use=="Pastures" | Land.use=="Crops" | Land.use=="Scrub" | Land.use=="Kans Grass" | Land.use=="Towns" | Land.use=="Barren Soil", "non_forest" 
                              , "other"))]

land_use_fig=land_use_fig[type=="forest" | type== "non_forest"]

col_sum=colnames(land_use_fig)[3:5]
land_use_fig[,(col_sum):=lapply(.SD, sum), by=c("River", "type"), .SDcols=col_sum]
land_use_fig=unique(land_use_fig, by=c("type", "River"))

land_use_fig=land_use_fig[,.(River, type, X2003, X2008, X2012)]
land_use_fig=rbind(land_use_fig, net)

setkey(land_use_fig, River)
land_use_fig=land_use_fig[,.(River, type, X2003, X2008, X2012)]
land_use_fig=melt(land_use_fig, id=c("River", "type"))
land_use_fig[, variable:=ifelse(variable=="X2003", 2003, ifelse(variable=="X2008", 2008, 2012))]
foo_d=land_use_fig[variable==2003, value]
land_use_fig[, foo:=foo_d]
land_use_fig[, foo:=value - foo]

lu_fig1<- ggplot(land_use_fig[type=="forest"], aes(x=factor(variable), y=foo, group=River, col=River))+
  geom_point(size=2)+
  geom_line(size=1.2)+
  theme_bw()+
  xlab("Year")+
  ylab("Ha")+
  ggtitle(paste("forest land"))+
  theme(
    legend.position = "bottom"
  )


lu_fig2<- ggplot(land_use_fig[type=="non_forest"], aes(x=factor(variable), y=foo, group=River, col=River))+
  geom_point(size=2)+
  geom_line(size=1.2)+
  theme_bw()+
  xlab("Year")+
  ylab("Ha")+
  ggtitle(paste("non forest land"))+
  theme(
    legend.position = "bottom"
  )


lu_fig3<- ggplot(land_use_fig[type=="net"], aes(x=factor(variable), y=foo, group=River, col=River))+
  geom_point(size=2)+
  geom_line(size=1.2)+
  theme_bw()+
  xlab("Year")+
  ylab("Ha")+
  ggtitle(paste("net forest cover"))+
  theme(
    legend.position = "bottom"
  )


###### >>>>> I need to get back to this and add them to the figure with ESE estimates as bars <<<<<<<<<

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ####
########                                  Plot PIEA polygons                                                 ###########
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
county_fills <- readOGR(dsn="C:/Users/mr2284/Dropbox/Research/Panama Canal-My material/Codes/IE/IE_PCW/Data/Watersheds",layer="watersheds_original")

county_fills@data$id = rownames(county_fills@data)
county_fills_2= county_fills@data

PIEA@data$id = rownames(PIEA@data)
PIEA_2= PIEA@data

# install.packages("gpclib")
# gpclibPermit() ## It should return TRUE

county_fills_1 <- tidy(county_fills, region = "id")
fills.df = join(county_fills_1, county_fills@data, by="id")

PIEA_1  <- tidy(PIEA, region = "id")
pills.df = join(PIEA_1, PIEA@data, by="id")

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ####
########                                  Data Analysis           ###########
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
trin     = watershed_PIEA_final_by_watershed[,SUBCUENC_2][25]
ciri     = watershed_PIEA_final_by_watershed[,SUBCUENC_2][31]
cano     = watershed_PIEA_final_by_watershed[,SUBCUENC_2][3]
Boqueron = watershed_PIEA_final_by_watershed[,SUBCUENC_2][4]
Gatun    = watershed_PIEA_final_by_watershed[,SUBCUENC_2][8]

watershed_PIEA_west = watershed_PIEA_final_by_watershed[SUBCUENC_2==trin | SUBCUENC_2==ciri | SUBCUENC_2==cano | SUBCUENC_2==Boqueron | SUBCUENC_2==Gatun]

watershed_PIEA_west = watershed_PIEA_west[ SUBCUENC_2==trin,     SUBCUENC_2:="Trinidad"]
watershed_PIEA_west = watershed_PIEA_west[ SUBCUENC_2==ciri,     SUBCUENC_2:="Ciri grande"]
watershed_PIEA_west = watershed_PIEA_west[ SUBCUENC_2==cano,     SUBCUENC_2:="Cano Quebrado"]
watershed_PIEA_west = watershed_PIEA_west[ SUBCUENC_2==Gatun,    SUBCUENC_2:="Gatun"]
watershed_PIEA_west = watershed_PIEA_west[ SUBCUENC_2==Boqueron, SUBCUENC_2:="Boqueron"]

river_discharge_west= river_discharge[River=="Trinidad" | River=="Ciri grande" | River=="Cano Quebrado" | River=="Boqueron" | River=="Gatun"]
river_discharge_west=river_discharge_west[date_disch < Dry_season_end_date]
river_discharge_west[, tot_discharge := discharge_m3_s*24*3600]  # M3

setkey(watershed_PIEA_west, SUBCUENC_2)
setkey(river_discharge_west, River)

watershed_PIEA_west=watershed_PIEA_west[river_discharge_west]
data_pre=watershed_PIEA_west[year < 2008]

data_pre[, discharge_per_ha := tot_discharge/V2] # m3 per day per hectare
data_pre[, extra_discharge  := discharge_per_ha * V1 * .2] # m3 per day for the entire catchment under 20% ESE
data_pre[, mean_extra_discharge :=mean(extra_discharge), by=c("SUBCUENC_2", "month")]
data_pre[, sd_extra_discharge   :=sd(extra_discharge), by=c("SUBCUENC_2", "month")]
data_pre=unique(data_pre, by=c("SUBCUENC_2", "month"))

data_pre=data_pre[,.(SUBCUENC_2, month, mean_extra_discharge, sd_extra_discharge)]

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ####
#                   0. Teeatment before and after ####
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#################
data_reg_copy_daily = copy(data_reg)
data_reg_copy_daily[,total_rain_day:=mean(total_rain_day), by=c("River", "year", "month", "day")]
data_reg_copy_daily=unique(data_reg_copy_daily, by=c("River", "year", "month", "day"))
data_reg_copy_daily[, tot_discharge  := discharge_m3_s*24*3600] # total daily Million m3
data_reg_copy_daily[, lag.rain_day   := c(NA, total_rain_day[-.N]), by=c("SUBCUENC_2", "year")]
data_reg_copy_daily[, lag.rain_day_2 := c(NA, lag.rain_day[-.N]),   by=c("SUBCUENC_2", "year")]
data_reg_copy_daily[, rain_past_2_days := lag.rain_day + lag.rain_day_2]
data_reg_copy_daily[, lag.discharge  := c(NA, tot_discharge[-.N]),  by=c("SUBCUENC_2", "year")]
data_reg_daily_dry = data_reg_copy_daily[dry_dummy==1]
data_reg_daily_wet = data_reg_copy_daily[dry_dummy==0]

# 
# FN_before_after_by_river     <- function(year_pre, year_post, River_tr) {
#   # dt=data_reg_copy_daily[(River=="Trinidad" | River=="Ciri grande" | River=="Cano Quebrado")]
#   dt=data_reg_copy_daily[(River==River_tr)]
#   dt = dt[year < year_pre | year > year_post][ ,year_treat:= ifelse(year>2007, 1, 0)]
#   coefs_DiD = data.table(month=1:12, coefficient_DiD = rep(0 , 12), standard_error_DiD= rep(0, 12))
#   for(i in 1:12){
#     DiD_prepost = lm(tot_discharge ~ year_treat + total_rain_day + lag.rain_day + day_of_season + lag.discharge, 
#                      data = dt[ month == i])
#     beta_DiD = summary(DiD_prepost)$coefficients[2,1]
#     std_error= summary(DiD_prepost)$coefficients[2,2]
#     coefs_DiD[i, 2] = beta_DiD
#     coefs_DiD[i, 3] = std_error
#   }
#   
#   dt_ESE=data_pre[SUBCUENC_2==River_tr]
# 
#   l=ggplot(data = coefs_DiD, aes(x=factor(month), y=coefficient_DiD))+
#     geom_errorbar(aes(ymin=coefficient_DiD - 2.866 * standard_error_DiD , ymax=coefficient_DiD + 2.866 * standard_error_DiD), width=.1) +
#     geom_line(aes(group=1)) +
#     geom_point() +
#         geom_errorbar(data = dt_ESE, aes(y=mean_extra_discharge, ymin=mean_extra_discharge - 1.96 * sd_extra_discharge , ymax=mean_extra_discharge + 1.96 * sd_extra_discharge), 
#                   width=.2, col="red") +
#     theme_bw()+
#     xlab("month")+
#     ylab("Diff in Diff Coefficient")+
#     ggtitle(paste("Before", year_pre, "and after", year_post, "\nfor", River_tr, sep = " "))
#   return(l)
# }
# 
# 



FN_before_after_by_river     <- function(year_pre, year_post, River_tr) {
  # dt=data_reg_copy_daily[(River=="Trinidad" | River=="Ciri grande" | River=="Cano Quebrado")]
  dt=data_reg_copy_daily[River==River_tr & month < 5]
  dt = dt[year < year_pre | year > year_post][ ,year_treat:= ifelse(year>2007, 1, 0)]
  dt_pre=dt[year_treat==0 ,.(year, month, day, tot_discharge)]
  dt_pos=dt[year_treat==1 ,.(year, month, day, tot_discharge)]
  
  dt_pre[,mean_disch_pre:=mean(tot_discharge), by="month"]
  dt_pre[,foo:=.N, by="month"]
  dt_pre[,sd_disch_pre  :=  sd(tot_discharge), by= "month"]
  dt_pre[,sd_disch_pre  :=  (sd_disch_pre)^2/foo]
  dt_pre=unique(dt_pre, by="month")
  dt_pre=dt_pre[,.(month, mean_disch_pre, sd_disch_pre)]
  
  dt_pos[,mean_disch_pos:=mean(tot_discharge), by="month"]
  dt_pos[,foo:=.N, by="month"]
  dt_pos[,sd_disch_pos  :=  sd(tot_discharge), by= "month"]
  dt_pos[,sd_disch_pos  :=  (sd_disch_pos)^2/foo]
  dt_pos=unique(dt_pos, by="month")
  dt_pos=dt_pos[,.(month, mean_disch_pos, sd_disch_pos)]
  
  setkey(dt_pre, month)
  setkey(dt_pos, month)
  dt=dt_pre[dt_pos]
  dt[, sd:=sqrt(sd_disch_pre + sd_disch_pos)]
  dt[, mean:=mean_disch_pos - mean_disch_pre]
  
  dt_ESE=data_pre[SUBCUENC_2==River_tr & month < 5]
  
  l=ggplot(data = dt, aes(x=factor(month), y=mean))+
    geom_errorbar(aes(ymin=mean - 1.96 * sd , ymax=mean + 1.96 * sd), width=.1) +
    geom_line(aes(group=1)) +
    geom_point() +
    geom_errorbar(data = dt_ESE, aes(y=mean_extra_discharge, ymin=mean_extra_discharge - 1.96 * sd_extra_discharge , ymax=mean_extra_discharge + 1.96 * sd_extra_discharge), 
                  width=.2, col="red") +
    theme_bw()+
    xlab("month")+
    ylab("Change in daily discharge (m3)")+
    ggtitle(paste("Before", year_pre, "and after", year_post, "\nfor", River_tr, sep = " "))
  return(l)
}



## West Side
a1=FN_before_after_by_river(2008, 2012, "Trinidad")
a3=FN_before_after_by_river(2008, 2012, "Ciri grande")
a2=FN_before_after_by_river(2008, 2012, "Cano Quebrado")


a4=FN_before_after_by_river(2008, 2012, "Boqueron")
a5=FN_before_after_by_river(2008, 2012, "Chagres")
a6=FN_before_after_by_river(2008, 2012, "Gatun")
a7=FN_before_after_by_river(2008, 2012, "Pequeni")


```
## Introduction

Most studies of the program evaluation of PES programs have focused on changes in forest cover as a procy for the hydrological ecosystem services ( [Borner et al, 2017](http://www.sciencedirect.com/science/article/pii/S0305750X17300827#b0225)). Here, we directly focus on the ecosystem services in question, i.e. river discharge during dry and wet seasons (and potentially sediment load) for the Panama Canal Watershed. For hydrological services or forests, it is important to study the changes at the policy relevant scale, i.e. watershed scale. 



[Alix-Garcia et al. (2012)](http://le.uwpress.org/content/88/4/613.refs) studied the impact of PES program in Mexico which aimed at providing hydrological services through forest conservation. They used applicant pool to create the counterfactual, i.e. those who got the payment vs those who didn't. 
They found that deforestation rates were 50% lower in enrolled parcels, but that deforestation rates were generally low, which suggested that potential additionality was limited to begin with.

<!-- The evaluated outcomes are often proxies of actual environmental services, such as forest cover, through which programs aim at achieving additional service provision (e.g., carbon sequestration). --> 



## Study Area and Data

Sources of data:

+ PIEA parcels
+ hourly rainfall 2004 to 2015
+ daily discharge from hydrology yearbook
+ land cover for 2003, 2008 and 2012 from the ACP
+ start of the dry season date from the ACP
+ PCW watersheds

### Distribution of PIEA hectares across the watershed 

We can see that most of the changes have taken place in the western side of the watershed.

note that we do not have discharge data for all the watersheds that include hectares enrolled in the PIEA program, so even though some catchments have had significant participation (area-wise), we do not observe changes of cischarge in those catchments. Same is valid for control catchments.

```{r, echo=FALSE, warning=FALSE}
ggplot(fills.df) + 
  aes(x=long,y=lat, group=group) +
  geom_polygon(fill= NA) +
  geom_path(color="black") +
  geom_polygon(data = pills.df, aes(x=long,y=lat, group=group), fill="red") +
  geom_path(data = pills.df, aes(x=long,y=lat, group=group), color="red") +
  coord_equal(ratio=1) +
  labs(x="", y="") +
  # scale_fill_gradient(name = "Change in Well Yield",low = "#ff4444", high = "#ffffcc", 
  #                     space = "Lab", na.value = "grey50",
  #                     guide = "colourbar")+
  #  scale_fill_brewer("Utah Ecoregion")+
  #  labs(title="Change in well capacity in Nebraska and Kansas portion of High Plains Aquifer")+
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(), 
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.background = element_rect(fill='white')
  )


```


### Changes in land use covers from 2003 to 2012

Figures below show changes in forested and non-forested land covers across watersheds. Forest cover includes, mature forest, secondary forest, and plantations, while non-forest land includes pasture, crops, scrub, canal gras, towns, and barren soil that potentially have larger rainy season discharge and smaller sponge effect. 
2008 can be taken as the baseline for the project, so if we trust the land cover maps, 2003 to 2008 show the pre-treatment changes in land use in each of the watersheds.

We can see that the eastern watersheds except Chagres have lost forest cover, while western catchments have gained forest cover. Cano Quebrado has had small changes in forest cover. 
The increase in non-forest land has also been increasing in the eastern catchments. Cano Quebrado has also expirienced increase in non-forest land which is mainly towns and crop lands. In total, Ciri Grande and Trinidad are the only catchments that have gained forest land while the other catchments have lost forest land cover. Using only PIEA hectares and taking Trinidad and Ciri Grande as treatment and others as control should provide us with an upper bound on the effect of land use changes on ecosystems of interest.

<span style="color:red"> Provide number of hectares in each watershed. </span>

```{r, echo=FALSE, warning=FALSE, fig.height=11}
grid_arrange_shared_legend(lu_fig1, lu_fig2, lu_fig3)

```


### Summary Statistics


The number of hectares enrolled is at least comparable to the study by [Alix-Garcia et al. (2012)](http://le.uwpress.org/content/88/4/613.refs).




## Changes in daily discharge before and after treatment

Figures below show the treatment coefficient for each catchment. The unit of observation is daily discharge volume in cubic meters. The treatmment year is assumed to be 2008 since the PIEA program went into effect (approximately) around 2008. Before 2008 and after 2012 on the grphs simply means that we are comparing 2004-2007 as pre-treatment and 2012-2015 as post-treatment years. These graphs show the changes in for each catchment lumped by the month.
No controls are included in these regressions. The coefficient basically compare the average daily discharge before and after the treatment for each month. The standard errors have been boosted to consider for the fact that we picked each month as a sample.



The first three figures show the changes in daily discharge on the west side of the canal. What these figures show is the distribution of difference in mean of daily discharge before 2008 and after 2012 in black and expected increase in discharge under 20% ESE in red for the dry season. The red bars basically show:

$$
\frac{hectares\;\; in\;\; PIEA}{total\;\;hectares\;\;in\;\;catchment} \times baseline\;\;daily\;\;discharge
$$
in the pre-treatment period (before 2008). The variation comes from the variation of daily discharge at each month.

Ciri Grande and Trinidad had the most intensive PIEA participation hectares, while Cano Quebrado almost did not have any program related land use change. However, as we can see the changes are not distinguishable from zero. Cano Quebrado is perhaps the best control for these two catchments as it is in the western side of the canal. A quick look at the figures suggest small treatment effects. 

```{r, echo=FALSE, warning=FALSE}
## West Side
multiplot(a1, a2, a3, cols=2)
```

Next four figures show the changes in daily discharge on the east side of the canal:

```{r, echo=FALSE, warning=FALSE}
## East Side
multiplot(a4, a5, a6, a7, cols=2)

```

## Diff-in-Diff estimates:



## Next Steps

What is the explanation behind small changes in discharge?

+ Did PIEA result in land use changes? It's possible that PIEA did not change land uses. compare land use for PIEA polygons before and after treatment. Also we can do matching since we have the actual parcels in the Ciri Grande and Trinidad catchments, but this is more of an additionality story.
+ Are there other deforestation activity that cancled out the effect of agroforestry programs?
+ Is it possible that low quality lands participated in the program?

Compare changes from 2004 to 2008 to changes from 2008 to 2013 

explore sediment volume as the other dependent variable





